Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2022-10-28 analysis/paper/paper.Rmd
Add computational details about the paper itself
Clarify closing statment

Without the code used to generate the paper and the data that were gathered for the paper, we as a community cannot adequately evaluate the work as it is presented.
That is, while we may be standing on the shoulders of giants in doing our work, we cannot see where they have been to do our work, which hinders our efforts to be able to see farther ahead.

@@

# Data and Code Availability

@@

>>>>

Without the code used to generate the paper and the data that were gathered for the paper, we as a community cannot adequately evaluate the work as it is presented.
So, while we may be standing on the shoulders of giants as we are doing our work, when we cannot see where they have been by examining the code and data, it hinders our efforts to move plant pathology forward.

@@

# Technical Details

@@

## Computational Details

All relevant computational information (R and package versions, operating system) are given in the Methods for the data gathering and analysis.
The relevant details for this article itself are shown here.

```{r article-details}
pander::pander(sessionInfo())
```
